A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-12 PPSN2016/paper.Rnw
Intro looks good

\begin{abstract}
In a volunteer distributed computing system, users run a program in
their own machine to contribute to a common effort. If they are
embedded in a web page, collaboration is easy, but also ephemeral. In
this paper we analyze a volunteer evolutionary computing system called
NodIO and try to find out a few rules that encourage volunteer
participation and how to make the most of their contributions to the
evolutionary algorithm. We will show different measures of
participation and contribution to the algorithm and how different
volunteer usage patterns and tweaks in the algorithm contribute to
improvements and leveraging of these contributions. 
\end{abstract}

@@

The world wide web provides not only a platform for content
distribution, but an increasingly reliable and high-performance
platform for running distributed applications. This is based in two
key facts: the Javascript virtual machine every browser runs and a
simplified standard interface for interacting with servers. Thus
creating a distributed computing experiment is just a matter of making
a JavaScript application interchange information with a server, called
rest. From the point of view of the programmer, this involves
relatively common skills and no special libraries, since that
interface is built in the browser, and a simple application that
responds to those requests on the server side; both involve just a few
dozens lines of code additionally to whatever business logic your
application has. But, more importantly and from the point of view of
the user, that application can be run by simply visiting a web page.

>>>>

\begin{abstract}
In a volunteer distributed computing system, users run a program in
their own machine to contribute to a common effort. If the program is
embedded in a web page, collaboration is easy, but also ephemeral. In
this paper we analyze a volunteer evolutionary computing system called
NodIO and try to find out a few rules that encourage volunteer
participation and how to make the most of their contributions to the
evolutionary algorithm. We will show different measures of
participation and contribution to the algorithm and how different
volunteer usage patterns and tweaks in the algorithm contribute to
improvements and leveraging of these contributions. 
\end{abstract}

@@

The world wide web not only provides a platform for content
distribution, but also an increasingly reliable and high-performance
platform for running distributed applications. This is based in two
key facts: the Javascript virtual machine every browser runs and a
simplified standard interface for interacting with servers. Thus
creating a distributed computing experiment is just a matter of making
a JavaScript application interchange information with a server, called
REST. From the point of view of the programmer, this involves
relatively common skills and no special libraries, since that
interface is built in the browser, and a simple application that
responds to those requests on the server side; both involve just a few
dozens lines of code additionally to whatever business logic your
application has. But, more importantly and from the point of view of
the user, that application can be run by simply visiting a web page.
